---
title: "manipulateWidget Demo"
output: html_document
runtime: shiny
---

Hodor. Hodor hodor... Hodor hodor hodor hodor. Hodor, hodor. Hodor. Hodor, hodor, hodor. Hodor hodor?! Hodor, hodor. Hodor. Hodor, hodor - hodor hodor! Hodor, hodor, hodor. Hodor hodor hodor. Hodor. Hodor hodor - hodor... Hodor hodor hodor hodor; hodor hodor? Hodor. Hodor HODOR hodor, hodor hodor... Hodor hodor hodor; hodor hodor?! Hodor hodor - hodor hodor; hodor hodor; hodor hodor? Hodor hodor - hodor hodor... Hodor hodor hodor hodor. Hodor. Hodor hodor HODOR! Hodor HODOR hodor, hodor hodor - hodor hodor! Hodor hodor HODOR! Hodor hodor, hodor. Hodor hodor; hodor hodor; hodor hodor - hodor, hodor, hodor hodor. 

```{r, echo = FALSE, message = FALSE}
library(plotly)
library(manipulateWidget)
mydata <- data.frame(x = 1:100, y = rnorm(100))

myPlot <- function(type, lwd) {
  if (type == "points") {
    plot_ly(mydata, x= ~x, y = ~y, type = "scatter", mode = "markers")
  } else {
    plot_ly(mydata, x= ~x, y = ~y, type = "scatter", mode = "lines", 
            line = list(width = lwd))
  }
}

manipulateWidget(
  myPlot(type, lwd),
  type = mwSelect(c("points", "lines"), "points"),
  lwd = mwSlider(1, 10, 1, .display = type == "lines"),
  .height = 600
)
```

Hodor. Hodor hodor... Hodor hodor hodor hodor. Hodor, hodor. Hodor. Hodor, hodor, hodor. Hodor hodor?! Hodor, hodor. Hodor. Hodor, hodor - hodor hodor! Hodor, hodor, hodor. Hodor hodor hodor. Hodor. Hodor hodor - hodor... Hodor hodor hodor hodor; hodor hodor? Hodor. Hodor HODOR hodor, hodor hodor... Hodor hodor hodor; hodor hodor?! Hodor hodor - hodor hodor; hodor hodor; hodor hodor? Hodor hodor - hodor hodor... Hodor hodor hodor hodor. Hodor. Hodor hodor HODOR! Hodor HODOR hodor, hodor hodor - hodor hodor! Hodor hodor HODOR! Hodor hodor, hodor. Hodor hodor; hodor hodor; hodor hodor - hodor, hodor, hodor hodor. 

```{r, echo = FALSE, message = FALSE}
library(plotly)
library(manipulateWidget)
mydata <- data.frame(x = 1:100, y = rnorm(100))

myPlot <- function(type, lwd) {
  if (type == "points") {
    plot_ly(mydata, x= ~x, y = ~y, type = "scatter", mode = "markers")
  } else {
    plot_ly(mydata, x= ~x, y = ~y, type = "scatter", mode = "lines", 
            line = list(width = lwd))
  }
}

manipulateWidget(
  myPlot(type, lwd),
  type = mwSelect(c("points", "lines"), "points"),
  lwd = mwSlider(1, 10, 1, .display = type == "lines"),
  .height = 600
)
```
